From Freebase to Wikidata: The Great Migration

### 2015-10-16 paper.tex
capitalize Foundation in Wikimedia Foundation

The objective of the back-end was to have a~REST API allowing us
to serve data efficiently to the front-end of the tool and
providing statistical data about the approvals and rejections done over time.
As the resources of the Wikimedia foundation are limited,
the back-end was implemented in highly optimized C++
and runs as a~FastCGI application in the lighttpd Web server.
\autoref{fig:architecture} shows the overall architecture of the Primary Sources tool.

>>>>

The objective of the back-end was to have a~REST API allowing us
to serve data efficiently to the front-end of the tool and
providing statistical data about the approvals and rejections done over time.
As the resources of the Wikimedia Foundation are limited,
the back-end was implemented in highly optimized C++
and runs as a~FastCGI application in the lighttpd Web server.
\autoref{fig:architecture} shows the overall architecture of the Primary Sources tool.
